---
title: "R Markdown Workshop"
subtitle: "Reproducible Reports"
author: "Emi Tanaka"
date: "19th November 2019"
output: 
  html_document: 
    theme: default
---

The following are texts from Xie (2013) Dynamic Graphics and Reporting for Statistics. *PhD Thesis*.

# Dynamic reporting



Statistics as a scientific discipline has a dynamic nature, which can be observed in
many statistical algorithms and theories as well as in data analysis. For example, asymptotic
theories in statistics are inherently dynamic: they describe how a statistic or an
estimator behaves as the sample size increases. Data analysis is almost never a static
process. Instead, it is an iterative process involving cleaning, describing, modeling, and
re-cleaning the data. Reports may end up being re-written due to changes in the data
and analysis.


A dynamic document is a mixture of normal
text and program code; when we compile the document, the code is executed and turned
into results. In the end, the results from computing and the original text are combined
to form a report.

# Literate Programming

Statistical reporting is often the last step of data analysis, and traditionally it is separated
from the computing, i.e., we finish all the computations and collect the results
before we write the report. This is not only more  **demanding in terms of manual work, but also error-prone**. The paradigm of literate programming (Knuth, 1984) was brought
forward in the 1980s to write software and documentation, and later it was incorporated
into the R language as the well-known tool named Sweave (Leisch, 2002) for writing
statistical reports. However, Sweave is not a complete implementation of literate programming,
as pointed out by Schulte et al. (2012), and it lacks many useful features in
statistical reporting such as caching and full integration with the capabilities of R graphics.
Literate programming is often related to reproducible research, because the results
are generated directly from computer code and it is easy to re-run the code to get the
same results. 

# Animation 

Animations can add insight and interest to traditional static approaches to teaching
statistics and reporting, making statistics a more interesting and appealing subject.

Traditional static printed statistical reports have severe limitations, for conveying results
with some degree of complexity to an audience that is not trained to understand
the statistical ideas. Here, an active animated way to present results can help greatly. The
human visual cortex is arguably the most powerful computing system to which we have
access. Visualization puts information in a form that uses the power of this computing
system. By virtue of our visual system, we may be able to quickly understand a complicated
method or result, or at least a simplified case. Wender and Muehlboeck (2003)
showed the advantages of animations in teaching statistical topics like least squares and
type I & II errors. Velleman and Moore (1996) discussed a set of animation ideas that
can be effective for a student to learn concepts actively. Animation can be helpful only
if it is used appropriately; Fisher (2010) mentioned several successful applications of animations
such as GapMinder (Rosling and Johansson, 2009), but also argued animation
could be very bad when used poorly – it is usually good for presentation but not for
exploration.

```{r example-animation, fig.show='animate', fig.width=6, fig.height=4, cache=FALSE, interval=0.5, aniopts="controls"}
library(animation)
conf.int(0.9, main = "Demonstration of Confidence Intervals")
```

```{r example-animation2, fig.show='animate', fig.width=6, fig.height=6, cache=FALSE, interval=0.2, aniopts="controls,loop"}
for (i in 1:50) {
    plot(x=i/10, y=i/10, xlim=c(0,5), ylim=c(0,5), pch=20, col="red", cex=5)
}
```
